The \dealii Library, Version 9.6

### 2024-09-23 9.6/paper.tex
Remove funding todo for JPT
update intro

\dealii version 9.6.0 was released August 11, 2024.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). \todo{Update license} Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
  \item Substantial performance improvements to the matrix-free and multigrid
   infrastructure (Section~\ref{sec:mf}).
  \item Different additions to the non-matching infrastructure (see
    Section~\ref{sec:nonmatching}). In particular, the new class
    \texttt{FERemoteEvaluation} provides support for evaluating
    finite element shape functions and solutions on parts of the
    domain stored by other MPI processes.
  \item Much work has gone into writing wrappers for \trilinos' \tpetra{}
    stack of linear algebra classes. \tpetra{} is \trilinos' \kokkos-based
    replacement for the now-deprecated \epetra{} stack. See
    Section~\ref{sec:tpetra} for more on this.
  \item Tool classes \texttt{TaskResult} and \texttt{Lazy} that provide ways to compute
    values on a separate thread or only when first accessed (Section~\ref{sec:tools}).
  \item There are six new tutorial programs, on checkpointing simulations
    (step-83), integrating time-dependent solvers with external time
    stepping libraries (step-86, using \petsc's \ts{} library), advanced
    point evaluation techniques (step-87), non-matching grids
    (step-89), and trace-based methods for PDEs on embedded surfaces
    (step-90). See Section~\ref{subsec:steps} for more details.
\end{itemize}
%

\todo[inline]{If we keep the section on relicensing
  (Section~\ref{sec:license}), mention it in the list above.}

@@

\todo[inline]{Jan Philipp: Anything to list here?}

>>>>

\dealii version 9.6.0 was released August 11, 2024. This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
terms of the \emph{GNU Lesser General Public License} (LGPL). The \dealii
project is in the process of relicsensing the library under the terms of
the \emph{Apache License} 2.0 with \emph{LLVM Exception}. Downloads are
available at \url{https://www.dealii.org/} and
\url{https://github.com/dealii/dealii}.

The major changes of this release are:
%
\begin{itemize}
  \item
    Substantial performance improvements to the matrix-free and multigrid
    infrastructure (Section~\ref{sec:mf}).
  \item
    Different additions to the non-matching infrastructure (see
    Section~\ref{sec:nonmatching}). In particular, the new class
    \texttt{FERemoteEvaluation} provides support for evaluating finite
    element shape functions and solutions on parts of the domain stored by
    other MPI processes.
  \item
    Much work has gone into writing wrappers for \trilinos' \tpetra{} stack
    of linear algebra classes. \tpetra{} is \trilinos' \kokkos-based
    replacement for the now-deprecated \epetra{} stack. See
    Section~\ref{sec:tpetra} for more on this.
  \item
    Tool classes \texttt{TaskResult} and \texttt{Lazy} that provide ways to
    compute values on a separate thread or only when first accessed
    (Section~\ref{sec:tools}).
  \item
    There are six new tutorial programs, on checkpointing simulations
    (step-83), integrating time-dependent solvers with external time
    stepping libraries (step-86, using \petsc's \ts{} library), advanced
    point evaluation techniques (step-87), non-matching grids (step-89),
    and trace-based methods for PDEs on embedded surfaces (step-90). See
    Section~\ref{subsec:steps} for more details.
  \item
    In Section~\ref{sec:license} we summarize the motivation and approach
    behind our relicensing effort to make \dealii available under the terms
    of the the Apache License 2.0 with LLVM Exception.
\end{itemize}
%

@@
